\skills{Research Scholar \hfill Jan 2026 --- Present}\\
\subtext{ML Alignment and Theory Scholars (MATS) \hfill Bekerley, CA, USA}
\vspace{-.2em}
Fully funded research scholar position under the ML Alignment and Theory Scholars (MATS)
program, working on interpretability and alignment of large language models.\\

\skills{Visiting Scholar \hfill Sept 2025 --- Oct 2025}\\
\subtext{National University of Singapore, Advisor: Prof. Tan Nguyen \hfill Singapore}
\vspace{-.2em}
Fully funded visit to NUS to collaborate on research with Prof. Tan Nguyen.\\

\skills{AI Research Engineer \hfill July 2024 -- Present}\\
\subtext{Torilab \hfill Hanoi, Vietnam}
\vspace{-0.2em}
\begin{xitemize}
    \item Research on controlling LLM behaviours via activation steering and related intervention methods.
    \item LLM fine-tuning (SFT, DPO), prompt engineering, and large-scale model serving (vLLM, sglang, LitServe).
    \item Developed core framework for customizable chatbots with memory, tool use, and multi-turn interactions.
    \item Additional work: engagement detection, diffusion-based image generation, multi-speaker diarization.
\end{xitemize}

\skills{AI Research Engineer \hfill Nov 2018 -- May 2024}\\
\subtext{Cinnamon AI \hfill Hanoi, Vietnam}
\vspace{-0.2em}
\begin{xitemize}
    \item Co-creator of \href{https://github.com/Cinnamon/kotaemon}{\textbf{kotaemon}} (24.7k+ {\scriptsize \faStar}), an open-source platform for local RAG applications.
    \item Developed RAG-based and LLM-powered applications for industry use cases.
    \item Research in Document Image Understanding: information extraction, cross-lingual pre-training, and model development.
    \item Published peer-reviewed papers; one Best Paper Award at DIL-ICDAR'21.
    \item Led data standardization initiatives and improved internal data management systems.
    \item Mentored engineers and contributed to technical knowledge sharing across teams.
\end{xitemize}

\skills{Undergraduate Research Assistant \hfill Aug 2017 --- Sep 2019}\\
\subtext{IOT Lab, UET - Vietnam National University}
\vspace{-.2em}
\begin{xitemize}
    \item \textbf{Predictive models for wellbore data using machine learning and statistical methods.}
    \begin{zitemize}
        \item Facies/rock type classification; Time-series Analysis; Permeability Regression; Integrated Prediction Error Filter Analysis (INPEFA) curve calculation; Cumulative and Federated Learning.
    \end{zitemize}
\end{xitemize}