\skills{AI Research Engineer \hfill July 2024 --- Present}\\
\subtext{\href{https://www.castalk.com}{Castalk}}
\vspace{-.2em}
\begin{xitemize}
    \item \textbf{Building AI avatars.}
    \begin{zitemize}
\item Conducting research on controlling LLMs' behaviours without prompting (i.e. activation steering).
\item LLMs fine-tuning (SFT, DPO, classification), prompt engineering, LLMs serving (vLLM, sglang,
LitServe) with dynamic batching.
\item Developing the core framework for the customizable chatbots with memory, tool use, dynamic
prompts and multi-turn interactions.
        \item Other random tasks: User's engagement detection with head-pose tracking; Image Generation with
Diffusion-based models and LoRAs; multi-speaker diartization.
    \end{zitemize}
\end{xitemize}

\skills{AI Research Engineer \hfill Nov 2018 --- May 2024}\\
\subtext{\href{https://cinnamon.ai}{Cinnamon AI}}
\vspace{-.2em}
\begin{xitemize}
    \item \textbf{Developed RAG-based applications.}
    \begin{zitemize}
\item Co-creator of \href{https://github.com/Cinnamon/kotaemon}{\textbf{kotaemon}}
(22.5k+ {\scriptsize \faStar}): An
        open-source tool for local RAG application built for both end users and developers.
        \item Built demos for LLM-powered applications targeting the Insurance domain.
    \end{zitemize}
    \item \textbf{Researched, developed, and implemented AI solutions for Document Image Understanding.}
    \begin{zitemize}
        \item Information Extraction and Cross-lingual adaptive pre-training for a
        low-resource language (Japanese).
        \item Created new technical assets by introducing new Information Extraction models that
        became the new standard for client projects. Increased the f1-score by 2\% - 7\%.
        \item Publish \href{https://scholar.google.com/citations?user=\gscholarid}{papers} on
        Information Extraction at peer-reviewed conferences, 1 Best Paper Award
        at DIL-ICDAR'21.
    \end{zitemize}
    \item \textbf{Developed data-driven products and processes.}
    \begin{zitemize}
        \item Implement synchronization and local version control for the internal
        data management system.
        \item Initiated data standardization, defined and implemented processes regarding data life cycle and organization.
        % \item Related skills: Data Management, Data-driven Development, Software Engineering.
    \end{zitemize}
    \item Other tasks: Support cross-department alignment; Conduct/Facilitate technical sharing sessions; Training/Mentoring.
\end{xitemize}

\skills{Undergraduate Research Assistant \hfill Aug 2017 --- Sep 2019}\\
\subtext{IOT Lab, UET - Vietnam National University}
\vspace{-.2em}
\begin{xitemize}
    \item \textbf{Predictive models for wellbore data using machine learning and statistical methods.}
    \begin{zitemize}
        \item Facies/rock type classification; Time-series Analysis; Permeability Regression; Integrated Prediction Error Filter Analysis (INPEFA) curve calculation; Cumulative and Federated Learning.
    \end{zitemize}
\end{xitemize}