\skills{\href{https://github.com/Cinnamon/kotaemon}{Kotaemon} (\textmd{22.5k+ \scriptsize \faStar}) - An open-source tool for
local RAG application. \hfill Jan 2024 --- May 2024}\\
\subtext{
    Open-source project, Co-creator
    \hfill
    \href{https://cinnamon.github.io/kotaemon/}{\faFileLines}
    \href{https://github.com/Cinnamon/kotaemon}{\faGithub}
}
\begin{zitemize}
    \item A local RAG-based tool for chatting with your documents. Built with both end users and developers in mind.
    \item For end users: A local Question Answering UI for RAG-based QA.
    \item For developers: A framework for building your own RAG-based QA pipeline.
\end{zitemize}


\skills{Data Utility Improvement Experiment for DECAF \hfill Oct 2022 --- Nov 2022}\\
\subtext{
    Personal research
    \hfill
    \href{https://github.com/lone17/DECAF/blob/main/main.pdf}{\faFileLines}
    \href{https://github.com/lone17/DECAF}{\faGithub}
}
\begin{zitemize}
    \item A personal research on Causal Inference, Algorithmic Fairness and specifically the paper \href{https://arxiv.org/abs/2110.12884}{DECAF: Generating Fair Synthetic Data Using Causally-Aware Generative networks}.
    \item Improved data utility of the DECAF method using alternating graph during synthesis while still achieving similar level of  fairness.
\end{zitemize}

\skills{Gender/Accent Classification for Vietnamese short voice recordings \hfill Aug 2018 --- Sep 2018}\\
\subtext{
    \href{https://challenge.zalo.ai}{Zalo AI Challenge 2018 \faUpRightFromSquare}
    \hfill
    \href{https://github.com/lone17/speech-processing}{\faGithub}
}
\begin{zitemize}
    \item Classify the speaker's voice in a recording (typically under 3 seconds) by gender and regional accent.
    \item \textbf{4th place} on the Private Leaderboard, achieved \textbf{79.208\%
        accuracy} in 10 days as an individual participant.
\end{zitemize}

% \skills{Electric Meter OCR \hfill Oct 2019 --- Nov 2019}\\
% \subtext{
%     University Coursework Project
%     \hfill
%     \href{https://github.com/lone17/electric-meter-ocr/blob/master/Report.pdf}{\faFileLines}
%     \href{https://github.com/lone17/electric-meter-ocr}{\faGithub}
% }
% \begin{zitemize}
%     \item Develop a solution for extracting the value on the dial from images of electric meters. The solution is meant to be used in embedded hardware.
%     \item Achieved \textbf{0.08 on edit distance} with total code size
%     \textbf{under 10MB} and processing time \textbf{under 0.3s/image}.
% \end{zitemize}
