%====================
% EXPERIENCE A
%====================
\skills{AI Researcher/Engineer \hfill Nov 2018 --- Present}\\
\subtext{Cinnamon AI \hfill Hanoi, Vietnam}
\begin{xitemize}
    \item \textbf{Researched, developed, and implemented AI solutions for client projects and internal usage.}
    \begin{zitemize}
        \item \textbf{Co-authored 3 peer-reviewed papers} on Key Information Extraction.
        \item \textbf{Developed AI solutions for Key Information Extraction on document images of a low-resource language}: Implemented MVLM pre-training task for LayoutLM (and variants), adapted the English pre-trained weights to a low-resource language (Japanese), pre-trained and fine-tuned it on several client data sets, which \textbf{increased the f1-score by 2\%  - 7\%}.
        \item \textbf{Developed solutions for localizing and extracting documents from scanned images containing multiple documents} using Image Processing techniques and Deep Learning models,  \textbf{achieved 85\%+ IoU score}.
        \item \textbf{Worked on Document Image Classification}, \textbf{over 85\% accuracy} achieved on a client data set with \textbf{20+ classes}.
        \item \textbf{Worked on Object Detection on Document Images}: such as detecting logos, stamps, check marks, etc.
        \item \textbf{Performed Data Synthesis/Augmentation} using image processing techniques for overcoming data shortage.
        \item Other: Benchmarked internal AI solutions, Text Segmentation, printed/handwriting OCR, handled AI pipeline on client projects, contributed to several internal libraries.
    \end{zitemize}
    \item \textbf{Developed data-driven products and processes.}
    \begin{zitemize}
        \item \textbf{Developed synchronization and local version control features} for the CLI tool, used by AI Engineers and Researchers to query data from a central database and manage the local copy.
        \item \textbf{In charge of data-related objectives on the department road map}: lead discussions, identify issues, propose solutions, decide action items for data centralization, data management, data integrity, labeling UI improvement, central database design, etc.
        \item \textbf{Taking part in revamping the internal data management system}: Develop a new standardized label format, redesign database schema, develop data sharing hub.
        \item \textbf{Initiated and took charge of data standardization}: defined and implemented processes regarding data life cycle and organization, enabling data sets from different client to be re-useable collectively.
    \end{zitemize}
    \item Other tasks: Supporting cross-department alignment; Conducting/Facilitating technical sharing sessions; Training/Mentoring;.
    \item Tools and technologies
    \begin{zitemize}
        \item Mainly used: \textbf{Python, Pytorch, Tensorflow/Keras, Transformers (Hugging Face), Git, OpenCV, Scikit-learn \LaTeX.}
        \item Also familiar with: DVC, Neptune, CircleCI, Jenkins, Docker, KubeFlow, Elasticsearch.
        \item Environments: GCP, AWS, Linux, Windows.
    \end{zitemize}
\end{xitemize}

%====================
% EXPERIENCE B
%====================
\skills{Undergraduate Research Assistant \hfill Aug 2017 --- Sep 2019}\\
\subtext{IOT Lab, University of Engineering and Technology - Vietnam National University, Hanoi \hfill Hanoi, Vietnam}
\vspace{-.2em}
\begin{xitemize}
    \item \textbf{Contributed to the Machine Learning Toolkit of the \href{https://www.i2g.cloud/well-insight}{Well Insight platform \faUpRightFromSquare}}
    \begin{zitemize}
        \item \textbf{Built predictive models for geophysical data} using machine learning and statical methods.
        \item Worked in conjunction with Front-end/Back-end Engineers and domain experts to ensure requirements are met.
        \item Problem worked on: Facies/rock type classification; Time series prediction on well-logs data; Permeability regression; Integrated Prediction Error Filter Analysis (INPEFA) curve calculation; Cumulative and Federated learning for well-logs data.
    \end{zitemize}
    \item Tools and technologies: Python, Keras/Tensorflow, OpenCV, Scikit-learn,XGBoost, Javascript.
\end{xitemize}

%====================
% EXPERIENCE E
%====================
%\subsection{{ROLE / PROJECT E \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company E \hfill somewhere, state}
%\begin{zitemize}
%\item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%\item Ut malesuada purus at mi placerat dapibus.
%\item Suspendisse finibus massa eu nisi dictum, a imperdiet tellus convallis.
%\item Nam feugiat erat vestibulum lacus feugiat, efficitur gravida nunc imperdiet.
%\item Morbi porta lacus vitae augue luctus, a rhoncus est sagittis.
%\end{zitemize}
