\skills{AI Researcher/Engineer \hfill Nov 2018 --- Present}\\
\subtext{Cinnamon AI \hfill Hanoi, Vietnam}
\begin{xitemize}
    \item \textbf{Developing LLMs-powered applications for Insurance Domain.}
    \begin{zitemize}
        \item Developing an internal framework for building RAG-based Question Answering applications: allowing
        users to build workflows that consists of LLM, Prompts, Vector Stores, Indexers and Retrievers,
        Agents, Output Parsers, etc.
        \item Built demos for LLM-powered applications targeting the Insurance domain.
        \item Related skills: Large Language Models, Prompt Engineering, Information Retrieval, Software
        Engineering, Business-oriented Development.
        \item Technologies used: OpenAI, Cohere, LangChain, LangFlow, Github Actions, HuggingFace, LlamaIndex, Haystack.
    \end{zitemize}
    \item \textbf{Researched, developed, and implemented AI solutions for Document Image Understanding.}
    \begin{zitemize}
        \item Published \href{https://scholar.google.com/citations?user=\gscholarid}{papers} at
        peer-reviewed conferences, including 1 Best Paper Award at DIL-ICDAR 2021.
        \item Key Information Extraction on document images low-resource languages:
        \vspace{.2em}
        \begin{zitemize}
            \item Implemented MVLM pre-training task for LayoutLM (and variants).
            \item Cross-lingual adaptive pre-training for a low-resource language (Japanese).
            \item Created new technical assets by introducing new Information Extraction models that
            became the new standard for client projects. Increased the f1-score by 2\% - 7\%.
        \end{zitemize}
        \item Document Image Classification, over 85\% accuracy achieved on a client data set with 20+ classes.
        \item Other: Document Segmentation; Document Object Detection (logos, stamps, check marks, etc.);
        Data Synthesis/Augmentation (Image Processing based); Text Segmentation;
        printed/handwriting OCR.
        \item Related skills: Research, Training/fine-tuning, Language Model Pre-training, Image Processing, Computer Vision, Natural Language Processing.
        \item Technologies used: Python, Pytorch, Tensorflow/Keras, Transformers (Hugging Face),
        OpenCV, Scikit-learn, \LaTeX, DVC, Neptune, CircleCI, Docker.
    \end{zitemize}
    \item \textbf{Developed data-driven products and processes.}
    \begin{zitemize}
        \item Worked on Data Management CLI tool: Synchronization and local version control, used by AI Engineers and Researchers to query data from a central database and manage the local copy.
        \item Roadmap planning for data-related objectives: lead discussions, identify issues, propose solutions, decide action items for data centralization, data management, data integrity, labeling UI improvement, etc.
        \item Initiated data standardization: defined and implemented processes regarding data life cycle and organization, enabling datasets from different client to be re-useable collectively.
        \item Related skills: Data Management, Label Schema Design, Data-driven Development, Software Engineering.
    \end{zitemize}
    \item Other tasks: Supporting cross-department alignment; Conducting/Facilitating technical sharing sessions; Training/Mentoring.
\end{xitemize}

\skills{Undergraduate Research Assistant \hfill Aug 2017 --- Sep 2019}\\
\subtext{IOT Lab, UET - Vietnam National University, Hanoi \hfill Hanoi, Vietnam}
\begin{xitemize}
    \item \textbf{Developed the Machine Learning Toolkit of an online wellbore data interpretation and management platform.}
    \begin{zitemize}
        \item Built predictive models for geophysical data using machine learning and statistical methods.
        \item Worked in conjunction with domain experts and FE/BE engineers to ensure requirements are met.
        \item Problem worked on: Facies/rock type classification; Time-series Analysis; Permeability Regression; Integrated Prediction Error Filter Analysis (INPEFA) curve calculation; Cumulative and Federated Learning.
    \end{zitemize}
    \item Related skills: Data Science, Machine Learning, Time-series Analysis.
    \item Technologies used: Python, Keras/Tensorflow, OpenCV, Scikit-learn, XGBoost, Javascript.
\end{xitemize}

%====================
% EXPERIENCE
%====================
%\subsection{{ROLE / PROJECT E \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company E \hfill somewhere, state}
%\begin{zitemize}
%\item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%\item Ut malesuada purus at mi placerat dapibus.
%\item Suspendisse finibus massa eu nisi dictum, a imperdiet tellus convallis.
%\item Nam feugiat erat vestibulum lacus feugiat, efficitur gravida nunc imperdiet.
%\item Morbi porta lacus vitae augue luctus, a rhoncus est sagittis.
%\end{zitemize}
